### 2013-10-02 src2/thesis.tex
apa
added missing file
thesis work

\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{lingmacros}
\usepackage{subfig}

@@

\newcommand{\bequ}{\begin{quote}}
\newcommand{\enqu}{\end{quote}}
\newcommand{\eop}[1]{\mbox{\sl #1}}
\newcommand{\sube}[2]{#1_{#2}}
\newcommand{\id}[1]{{\it #1}}
\newcommand{\kwd}[1]    {\mbox{\textbf{#1}}}
\newcommand{\str}[1]{{\id "#1"}}
\newcommand{\lemon}{\emph{lemon}}
\newcommand{\textt}[1]{\texttt{#1}}
\newcommand{\txttt}[1]{\texttt{#1}}

\renewcommand*{\thesection}{\arabic{section}}

@@

%\input{titlepage}

@@

\section*{Acknowledgements}
ACK ACK ACK

FUNDING FUNDING

@@

\clearpage{}
\section*{Additional Publications}

Papers not included in thesis

\bibliographystyle{splncs}
\bibliography{intro}

\chapter{Papers}

@@

@@

>>>>

%\usepackage{code}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{lingmacros}
\usepackage{subfig}

@@

%% \newcommand{\bequ}{\begin{quote}}
%% \newcommand{\enqu}{\end{quote}}
%% \newcommand{\eop}[1]{\mbox{\sl #1}}
%% \newcommand{\sube}[2]{#1_{#2}}
%% \newcommand{\id}[1]{{\it #1}}
%% \newcommand{\kwd}[1]    {\mbox{\textbf{#1}}}
%% \newcommand{\str}[1]{{\id "#1"}}
%% \newcommand{\lemon}{\emph{lemon}}
%% \newcommand{\textt}[1]{\texttt{#1}}
%% \newcommand{\txttt}[1]{\texttt{#1}}

%\renewcommand*{\thesection}{\arabic{section}}

\newcommand{\thesistitle}{Not decided upon}

@@

\begin{titlepage}
\begin{centering}
{\sc Thesis for the Degree of Doctor of Philosophy}
\vspace{30ex}

{\LARGE\bf\thesistitle}

\vspace{7ex}

\large Bo Joel Svensson
\vfill

\vspace{1cm}
\normalsize
{\sc Department of Computer Science and Engineering}\\
{\sc Chalmers University of Technology and G\"oteborg University}\\
G\"oteborg, Sweden 2013

\end{centering}
\end{titlepage}

@@

\section*{Acknowledgements}

\vspace{5mm}
This research has been funded by the Swedish Foundation for
Strategic Research (which funds the Resource Aware Functional 
Programming (RAW FP) Project) and by the Swedish Research Council.

@@

\section{Plan} 
\begin{itemize} 
  \item The Scope
  \item The Problem 
  \item The Methods
  \item The Results 
\end{itemize}

\begin{itemize} 
  \item The Context
  \item Lift head from details 
  \item Why are there interesting questions around parallelism and GPUs
  \item The Story
  \item Reflect on leassons learnt along the way 
  \item Tell a story around the papers 
  \item Future Work
\end{itemize}

\clearpage{}
%\section*{Additional Publications}

%Papers not included in thesis

%\bibliographystyle{plain}
%\bibliography{intro}

\chapter{GPU programming papers}

@@

% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------

\chapter{Retargetable parallel programming papers}
% ---------------------------------------------------------------------------
% 
% ---------------------------------------------------------------------------
\cleardoublepage

\section{Programming Future Parallel Architectures with Haskell and Intel ArBB}
%\addcontentsline{toc}{chapter}{Parallel Programming in Haskell Almost for Free}

\begin{center} 
Bo Joel Svensson, Ryan R. Newton
\end{center}

\input{./arbb/paperThesis}

@@

\bibliographystyle{plain}
\bibliography{thesis}
\addcontentsline{toc}{chapter}{Bibliography}
